Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-01 reviews/response.Rmd

---
title: Response to reviewers
author: "JCGS-20-344"
output:
  MonashEBSTemplates::memo:
    includes:
fontfamily: mathpazo
---

We would really like to thank the editor and the reviewers for their encouragement and detailed feedback which has helped to improve the paper in terms of both concision and precision as well as reaching out to more readers.
The point by point description of changes are below:

# Reviewer 1 comments {-}

Q1. I am not convinced that it is required to introduce the concept of grammar of graphics and embed the used visualization in this framework on such a level of detail like in Section 5. Of course some elements of the grammar of graphics are used in Section 5.2 to argue about facets, levels, aesthetic variables, and mappings, but if the reader does not know about this framework, the introduction and explanations about this concept/framework provided in Section 5 is not enough to follow the later argumentation. I would like to see some more details on the concept/framework on the grammar of graphics, or not using the concepts in the parts of Section 5.2 and paraphrasing it without using the terms from the grammar of graphics. I think that it is doable to explain the construction of the visualization without using this concept/framework, because the mappings are quite straight forward. I would like to see (a) either extend the introduction to grammar of graphics and the basics needed to argue in more detail about the embedding of your visualizations using this concept/framework, or (b) remove it.

@@

A1. Removed.

Q2. It is not clear from the paragraph in Section 5.1 what basic plot choices are implemented and used and supported for visualization. There is only the list of plots to display descriptive statistics provided. It would be important to describe which are implemented and possible to use. The later examples use primarily letter-value plots, then also box-plots, violin plots and line charts with area quantile plots. The letter-value plots are used in major examples of the paper, therefore I would argue to provide some more details on this visual representation and what the 5 colors and letters mean (e.g. LV=letter value, M = median, F = fourths, E = eighths, D = sixteenths, C = thirty-seconds), as it is not as widely known like standard box-plots. This would help greatly in better following the argumentation and explanations.

### 2021-05-09 main.Rmd
figure 4 correction

(ref:allFig) Distribution of energy consumption displayed through letter value plots: plot a across month-of-year faceted by quarter-of-year; plot b across weekday/weekend faceted by quarter-of-year; plot c across quarter-of-year faceted by weekday/weekend. Plot a shows a clash since there are empty combinations. Plots b and c show harmonies since each quarter include both weekdays and weekends. It can be seen in plot b that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter where the letter values below D and E behave differently. This is probably because of lower temperatures in the second quarter compared to the first quarter (summer in Australia). Plot c switches the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. 
<!-- For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends. -->

>>>>

(ref:allFig) Distribution of energy consumption displayed through letter value plots used to illustrate harmonies and clashes: (a) across month-of-year faceted by quarter-of-year; (b) across weekday/weekend faceted by quarter-of-year; (c) across quarter-of-year faceted by weekday/weekend. (a) shows a clash since there are empty combinations. (b) and (c) show harmonies since each quarter include both weekdays and weekends. It can be seen in (b) that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter.
For example, the letter value D for weekdays mostly corresponds to letter value E for weekends, implying there are lower values of energy consumption during weekdays in the second quarter. This is probably because of lower temperatures in the second quarter compared to the first quarter (summer in Australia). (c) switches the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. For example, the lower D and E letter values are most different across different quarters for weekdays and weekends respectively.
<!-- For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends. -->
